RELIKE: Reionization Effective Likelihood from Planck 2018 Data

### 2021-05-11 paper/rei.tex
fixed typo in taupc(15,30) <-->taupc(15,50) in conclusion; fixed error in .bib file.

    \item{The constraint on the high-redshift optical depth $\tau_{\rm PC}(15, 50) < 0.020$ (95\% C.L.) is also stable when extending $\zmax$ to 50: $\tau_{\rm PC}(15, 30) < 0.019$ (95\% C.L.).}

>>>>

    \item{The constraint on the high-redshift optical depth $\tau_{\rm PC}(15, 30) < 0.020$ (95\% C.L.) is also stable when extending $\zmax$ to 50: $\tau_{\rm PC}(15, 50) < 0.019$ (95\% C.L.).}
